### 2012-11-27 resumoeabstract.tex
arrumada lista de figuras, indo para arrumação de código

The representation of music's basic elements - such as notes, ornaments and intervalar structures - in terms of dicrete-time audio is used in software and routines for musical creation and sound design. Even so, there is no unified approach that relates directly this elements to the sound discrete-time samples. In this dissertation, each musical element is described by equations that result directly on the sonic time samples. The fundamental element, the musical note with duration, volume, pitch and timbre, is related quantitatively to the characteristics of the digital signal. Internal variations, such as tremolos, vibratos and spectral fluctuations are also considered, which enables the synthesis of notes inspired by real instruments and new sonorities. With this representation of notes, we predispose canonical resources for the generation of musical structures, such as rhythmic meter, pitch intervals and cycles. The equations gave rise to a computer toolbox: scripts that accomplish each equation and result simple sonic examples. We name \mass, Music and Audio in Sequences and Samples, this resources and its efficacy was confirmed by the synthesis of small musical pieces using basic notes, incremented notes and notes in music. It is possible, as well, to synthesize whole albums through collage of the scripts and parametrization specified by the user. With the paradigm of open source implementation, the \mass\ toolbox can be expanded in processes of co-authorship and used freely by musicians, engineers and other interested parties. In fact, the system was already employed by external users for diverse purposes which include music production, artistic presentations, psicoacoustic experiments and computer language diffusion by means of the playful appeal of audiovisual artifacts.

>>>>

The representation of the basic elements of music - such as notes, ornaments and intervalar structures - in terms of discrete audio signal is often used in software for music creation and design. Nevertheless, there is no unified approach that relates these elements to the sound discrete samples. In this dissertation, each musical element is described by equations that represent the sonic time samples, which are then implemented in scripts within a software toolbox, referred to as \massa\ (Music and Audio in Sequences and Samples). The fundamental element, the musical note with duration, volume, pitch and timbre, is related quantitatively to the characteristics of the digital signal. Internal variations, such as tremolos, vibratos and spectral fluctuations, are also considered, which enables the synthesis of notes inspired by real instruments and new sonorities. With this representation of notes, resources are provided for the generation of musical structures, such as rhythmic meter, pitch intervals and cycles. The efficacy of \massa\ was confirmed by the synthesis of small musical pieces using basic notes, incremented notes and notes in music. Also possible is to synthesize whole albums through collage of the scripts and parameterization specified by the user. With the paradigm of open source implementation, \massa toolbox can be expanded in co-authorship processes and used freely by musicians, engineers and other interested parties. In fact, \massa has already been employed by external users for diverse purposes which include music production, artistic presentations, psychoacoustic experiments and computer language diffusion where the appeal of audiovisual artifacts is exploited.
